### 2017-11-04 pkg/model4you/inst/JORS/man_model4you.Rnw
ylab and clean up Rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1676 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 99142485cdebba65dca043f41940f6e2ed11a4d4

To investigate whether the exam was fair, we asses whether the two groups
differ in terms of the percentage of correctly answered exam questions. This
can be done using a simple linear model regressing the percentage points of
correct anwers on the exam group. 
<<math_bmod>>=
bmod_math <- lm(pcorrect ~ group, data = MathExam)
@
The estimtates and confidence intervals of this model can be computed via
<<>>=
cbind(estimate = coef(bmod_math), confint(bmod_math))
@
% The estimtates and confidence intervals of this model are shown in 
% Table~\ref{tab:bmod}.
% <<math_bmod_coef, results="asis", echo=FALSE>>=
% library("Hmisc")
% cf <- round(cbind(estimate = coef(bmod_math), confint(bmod_math)), 2)
% colnams <- dimnames(cf)[[2]]
% colnams <- gsub("\\%", "\\\\%", colnams)
% colnams[1] <- "$\\theta$"
% 
% latex(cf,
%       booktabs = TRUE,
%       rowlabel = "", file = "", 
%       colheads = colnams,
%       label = "tab:bmod", caption = "Estimate and confidence intervals for the base model."
%       )
% @
%% <TH> warum brauchen wir die Abb 2x? Bitte nur einmal richtig ohne die
%% gg-Freuerei. /TH>
The model can be visualised by plotting the estimated densities
(see Figure~\ref{fig:math_bmod_vis}):
<<math_bmod_vis, fig.height=2.5, fig.width=5, out.width="0.7\\textwidth", fig.cap = "Density estimates of base model for the Mathematics Exam data.">>=  
lm_plot(bmod_math)
@
Both the estimates and confidence intervals and the density curves suggest
that there is almost no difference between the two groups. But does this
really hold for all types of students?
% As the plot is a \emph{ggplot2} graphic it can be maniulated with the usual
% \emph{ggplot2} layers, e.g.\ with
% <<eval=FALSE>>=
% lm_plot(bmod_math) + labs(y = "Estimated Density", x = "% Correct")
% @
% or equivalently with 
% <<eval=FALSE>>=
% myplot <- function(model, ...) {
%   lm_plot(model, ...) + 
%     labs(y = "Estimated Density", x = "% Correct")
% }
% myplot(bmod_math)
% @
% The result is shown in Figure~\ref{fig:math_bmod_vis} (b).
% <<math_bmod_vis, echo=FALSE, fig.cap = "Base model for Mathematics Exam data.", fig.subcap=c("Figure made with \\texttt{lm\\_plot()}.", "Figure made with manipulated \\texttt{lm\\_plot()}."), out.width="0.45\\textwidth", fig.height=3, fig.width=5>>=
% lm_plot(bmod_math)
% myplot <- function(model, ...) {
%   lm_plot(model, ...) + 
%     labs(y = "Estimated Density", x = "% Correct")
% }
% myplot(bmod_math)
% @

@@

ggplot(dpdat_math, aes(x = tests, y = group2)) +
  geom_point(alpha = 0.2, size = 1) + 
  geom_smooth(fill = NA, method = "loess") +
  theme(legend.position = "none") +
  ylab("individual estmated group effect")

ggplot(dpdat_math, aes(x = tests, y = group2, color = tests)) +
  geom_quasirandom(alpha = 0.5, size = 1) +
  theme(legend.position = "none") +
  ylab("individual estmated group effect")
@

@@

ggplot(dpdat_math, aes(x = attempt, y = group2, color = attempt)) +
  geom_quasirandom(alpha = 0.5) +
  theme(legend.position = "none") +
  ylab("individual estmated group effect")

ggplot(dpdat_math, aes(x = gender, y = group2, color = gender)) +
  geom_boxplot() +
  geom_quasirandom(alpha = 0.5) +
  theme(legend.position = "none") +
  ylab("individual estmated group effect")
@

>>>>

To investigate whether the exam was fair, we asses whether the two groups
differ in terms of the percentage of correctly answered exam questions. This
can be done using a simple linear model regressing the percentage points of
correct anwers on the exam group. 
<<math_bmod>>=
bmod_math <- lm(pcorrect ~ group, data = MathExam)
@
The estimtates and confidence intervals of this model can be computed via
<<>>=
cbind(estimate = coef(bmod_math), confint(bmod_math))
@
The model can be visualised by plotting the estimated densities
(see Figure~\ref{fig:math_bmod_vis}):
<<math_bmod_vis, fig.height=2.5, fig.width=5, out.width="0.7\\textwidth", fig.cap = "Density estimates of base model for the Mathematics Exam data.">>=  
lm_plot(bmod_math)
@
Both the estimates and confidence intervals and the density curves suggest
that there is almost no difference between the two groups. But does this
really hold for all types of students?

@@

ggplot(dpdat_math, aes(x = tests, y = group2)) +
  geom_point(alpha = 0.2, size = 1) + 
  geom_smooth(fill = NA, method = "loess") +
  theme(legend.position = "none") +
  ylab("estmated individual\nexam group effect")

ggplot(dpdat_math, aes(x = tests, y = group2, color = tests)) +
  geom_quasirandom(alpha = 0.5, size = 1) +
  theme(legend.position = "none") +
  ylab("estmated individual\nexam group effect")
@

@@

ggplot(dpdat_math, aes(x = attempt, y = group2, color = attempt)) +
  geom_quasirandom(alpha = 0.5) +
  theme(legend.position = "none") +
  ylab("estmated individual\nexam group effect")

ggplot(dpdat_math, aes(x = gender, y = group2, color = gender)) +
  geom_boxplot() +
  geom_quasirandom(alpha = 0.5) +
  theme(legend.position = "none") +
  ylab("estmated individual\nexam group effect")
@
